RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-05 review/response.tex

	\point Finally, the list of references is perhaps incomplete; many references do not include publication venues, while prior art backscatter radio, including coherent as well as non-coherent detection, structural mode, receiverless tags etc., both in terms of theory as well as experimentation, are not given. For example see work that bridges backscatter radio and RIS, including theory and experimental results for any number of tags and loads in the following: "Intelligently Wireless Batteryless RF-Powered Reconfigurable Surface: Theory, Implementation \& Limitations", IEEE Transactions on Wireless Communications (TWC), available as early access in ieeexplore, Nov. 2022, conference version available at IEEE Globecom 2021.
	\reply {We agree with the reviewer that the reference list could be improved. The current state of the art in BackCom is indeed very rich and diverse.  In the previous version of our manuscript, we only introduced papers that use RIS for backscatter modulation. In contrast, the recommended reference exploits commodity RFID tags, powered and controlled by a software-defined radio reader, to perform passive beamforming towards a legacy user at a different frequency. It validates the feasibility of using batteryless devices to adaptively enhance the SNR of the primary link. This reference makes the literature review more comprehensive, and we have added it in page~\pageref{m-cm:2.5} of the revised manuscript.}
\end{reviewer}

@@

\begin{reviewer}
	This paper introduces the concept of RIScatter, a unified architecture that combines Backscatter Communication (BackCom) and Reconfigurable Intelligent Surface (RIS) technologies, where the scatter nodes can modulate their own information and in the same time manipulate the wireless channel based on the information source, channel state information (CSI), and quality of service (QoS). The achievable primary-total-backscatter rate region in a single-user multi-node RIScatter system is investigated by designing the input distribution at scatter nodes, the active beamforming at the Access Point (AP), and the energy decision regions at the user. Numerical results show that RIScatter nodes can effectively utilize the scattered paths, enabling seamless transitions between backscatter modulation and passive beamforming techniques.

	The manuscript presents a novel concept, i.e., RIScatter, and studies an interesting problem. However, there are several problems with the manuscript, namely:

	\point Presentation and use of English: the presentation is sometimes unclear about the differences of RIScatter and existing techniques, it seems that the authors are concerned about listing the contributions in the introduction and forgot to contrast the key differences between existing approaches and the proposed RIScatter. Perhaps the authors can polish this part and make it more compact. Sometimes, a shorted and compact text can be made easier to understand. Moreover, there are too many poorly written sentences, typos and Grammar errors throughout the manuscript. It is not acceptable that a JSAC paper would feature with this level of English (especially coming from a British university!). Therefore, it is fundamental to improve the use of English and make sentences properly structured.
	\reply {We agree with the reviewer that the contrast between RIScatter and existing techniques could be clearer. The introduction and contribution have been refined in precise and explicit words for improved readability and clarity. Also, we have completely rewritten Section~\ref{m-sc:principles} on RIScatter principles to highlight the key differences between RIScatter and existing techniques. Remark~\ref{m-re:dynamic_passive_beamforming} now emphasizes the distinction and relationship between RIScatter and dynamic RIS. We also apologize for the poor English usage. The manuscript has been carefully proofread and revised to address the typos and grammar errors. We believe that the revised manuscript should be much easier to understand.}

	\point Literature review: the literature review on rate characterization for backscatter communications is deficient. Some recent and closely related works are missing:
	\begin{itemize}
		\item J. Qian, Y. Zhu, C. He, F. Gao and S. Jin, "Achievable Rate and Capacity Analysis for Ambient Backscatter Communications," in IEEE Transactions on Communications, vol. 67, no. 9, pp. 6299-6310, Sept. 2019.
		\item Z. Dai, R. Li, J. Xu, Y. Zeng and S. Jin, "Rate-Region Characterization and Channel Estimation for Cell-Free Symbiotic Radio Communications," in IEEE Transactions on Communications, vol. 71, no. 2, pp. 674-687, Feb. 2023.
		\item H. E. Hassani, A. Savard, E. V. Belmega and R. C. de Lamare, "Multi-user downlink NOMA systems aided by ambient backscattering: achievable rate regions and energy-efficiency maximization," in IEEE Transactions on Green Communications and Networking, 2023.
	\end{itemize}
	\reply {We appreciate your insightful comments on the reference list. Those papers have been incorporated into the literature review.}

@@

	\point Technical aspects: RIScatter is able to balance rate of primary transmission with rate of backscattered tags in a unified, user-controlled way, which brings technical advantages over existing approaches. This reviewer wonders why the authors only considered perfect CSI and did not assessed the impact of imperfect CSI on information rates (not the region!) given the limitations of tags and devices. Moreover, this reviewer is also sceptical about the assumption of perfect synchronization between the tags and the source. Can you explain why this is reasonable?
	\reply {Please kindly refer to response 2.1 for the discussion on imperfect CSI and response 2.2 for the discussion on perfect synchronization.}

	\point Simulation results: the authors opted for showing the results in terms of rate regions for several existing schemes and the proposed RISscatter. This is not properly motivated. Could explain why not include results such as information rates versus SNR or BER versus SNR?
	\reply {Thank you for the suggestion. In the previous version of the manuscript, we showed the impact of average noise power and disk radius on the achievable rate region. The former influences both primary and backscatter SNR, while the latter implicitly influences the backscatter SNR. In the revised manuscript, we have added explicit results on the achievable region vs primary SNR and backscatter SNR.
		Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary SNR can improve the primary rate but degrade the backscatter rate.
		The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
		This emphasizes the importance of accounting the primary-backscatter tradeoff in active-passive coexisting networks.
		Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter SNR increases.
		This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
		In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		The above results are added to Section~\ref{m-sc:simulation_results}.
		However, we do not include BER vs SNR because we have reached the page limit and the BER performance is not the focus of this paper. We appreciate your understanding in this matter.}

	\begin{figure}[!t]
		\centering
		\subfloat[Primary SNR\label{fg:region_snr_primary}]{
			\resizebox{0.48\columnwidth}{!}{
				\input{../assets/simulation/region_snr_primary.tex}
			}
		}
		\subfloat[Backscatter SNR\label{fg:region_snr_backscatter}]{
			\resizebox{0.48\columnwidth}{!}{
				\input{../assets/simulation/region_snr_backscatter.tex}
			}
		}
		\label{fg:region_config}
	\end{figure}
\end{reviewer}
